% LaTeX file for resume
% This file uses the resume document class (res.cls)
\let\nofiles\relax
\documentclass{res}
%\usepackage{helvetica} % uses helvetica postscript font (download helvetica.sty)
%\usepackage{newcent}   % uses new century schoolbook postscript font
\newsectionwidth{0pt}  % So the text is not indented under section headings
\usepackage{fancyhdr}  % use this package to get a 2 line header
\usepackage{graphicx}
\usepackage{hyperref}
\renewcommand{\headrulewidth}{0pt} % suppress line drawn by default by fancyhdr
\setlength{\headheight}{24pt} % allow room for 2-line header
\setlength{\headsep}{24pt}  % space between header and text
\setlength{\headheight}{24pt} % allow room for 2-line header
\pagestyle{fancy}     % set pagestyle for document
\rhead{ {\it P. Talbot}\\{\it p. \thepage} } % put text in header (right side)
\cfoot{}                                     % the foot is empty
\topmargin=-0.5in % start text higher on the page

\begin{document}
\thispagestyle{empty} % this page has no header
\name{Paul W. Talbot\\[12pt]}% the \\[12pt] adds a blank line after name

%\address{{\bf School Address} \\ Farris Engineering Center, Suite 209 \\
%  University of New Mexico \\   Albuquerque, NM 87106}

%\address{{\bf Home Address} \\ 3643 B Deloy Dr. \\Idaho Falls, ID 83401 \\ (509) 713-2842}
\address{3201 Florian Ave. \\Idaho Falls, ID 83401 \\ (509) 713-2842}




\begin{resume}

%\section{\centerline{OBJECTIVE}}
%\vspace{8pt} % provide vertical space between section title and contents
%A summer position with the MOOSE team at Idaho National Laboratory working on numerical methods.
\vspace{0.2in}
\section{\centerline{EDUCATION}}
\vspace{8pt}
{\sl Doctor of Philosophy}, Nuclear Engineering \\
University of New Mexico, Albuquerque, New Mexico, GPA 4.08 \hfill December 2016 \\
Thesis - Advanced Stochastic Collocation Methods for Polynomial Chaos in RAVEN
\begin{itemize} \itemsep -2pt
\item Researched, implemented multidimensional sparse grid sampling techniques
\item Distribution-specific polynomial fitting for uncertain variables
\item Vast statistical convergence improvement demonstrated for continuous responses
\item Development in Object-Oriented Python (RAVEN framework, github.com/idaholab/raven)
\item Software quality assurance, version control (Git)
\item Intership, Idaho National Laboratory
\end{itemize}

{\sl Master of Science}, Nuclear Engineering \\
Oregon State University, Corvallis, Oregon, GPA 3.75 \hfill March 2013 \\
Thesis - Extending the Discrete Maximum Principle for the IMC Equations
\begin{itemize} \itemsep -2pt
\item Research, implemented theoretical maximum for implicit Monte Carlo
\item Improved solve strategy for nonlinear photon transport
\item Intership, Los Alamos National Laboratory
\end{itemize}

{\sl Bachelor of Science}, Physics \\
BYU-Idaho, Rexburg, Idaho, GPA 3.84     \hfill    April 2010
\begin{itemize} \itemsep -2pt
\item Investigate down-blended vs fresh UO2 performance in BWR assembly
\item CASMO4, MICROBURN-B2, ALLADIN benchmarking
\item Power shapes, pin peaking, design limits
\item Intership, AREVA NP in Richland, WA
\end{itemize}


%\vspace{0.2in}
\section{\centerline{PROFESSIONAL EXPERIENCE}}
\vspace{8pt}

{\sl Idaho National Laboratory, Idaho Falls, ID} \\[2pt]
Principle Investigator \hfill 2020 - Present
\begin{itemize} \itemsep -2pt
  \item \emph{FORCE Software Development (github.com/idaholab/FORCE)} \\
  Identified priority research directions for modeling and simulation efforts across multiple Department
    of Energy (DOE) research programs, including Integrated Energy Systems and Light Water Reactor Sustainability.
  Negotiated scope of work with DOE managers for yearly project activities.
  Balanced labor and funding to execute yearly scope across multiple DOE programs and laboratories.
  Interviewed candidates for management, staff, postdoctoral, and internship positions.
  Led training for various software within Framework for Optimization of Resources and Economics (FORCE)
    tool suite.
  Presented work at conferences, both within energy industry and other industries such as data centers.
  Engaged with university, laboratory, and industry in leading or supporting proposals for new funding
    opportunities, including
    Nuclear Energy University Partnership (NEUP),
    Technology Commercialization Fund (TCF),
    Office of Clean Energy Demonstration (OCED),
    Gateway for Advanced Innovation in Nuclear (GAIN), and
    Advanced Research Projects Agency-Energy (ARPA-E).
\end{itemize} \vspace{-6pt}

Lead Software Developer \hfill    2017 - 2020
\begin{itemize} \itemsep -2pt
  \item \emph{HERON (github.com/idaholab/HERON)} \\
  Led a small team of developers in implementing HERON, a Python-based object-oriented plugin of RAVEN
  for stochastic techno-economic optimization of grid-energy systems. Planned, designed, and deployed
  software under continuous-deployment version control and software quality assurance. Provided training
  and deployed plugin for analyses of novel integrated energy system technologies in several markets,
   with partner industries, other national laboratories, and universities. Hosted interns annually
   and trained new staff in development practices.
  \item \emph{2021 LDRD awarded: Signal processing for cybersecurity} \\
  Managed a 3-year \$1.5M project including lab and university researchers to explore using high/low
  order correlation for false data injection detection in physical process signals, including
  toolset software development and demonstration on experimental systems.
\end{itemize} \vspace{-6pt}

Individual Contributor \hfill    2014 - 2017
\begin{itemize} \itemsep -2pt
  \item \emph{Sparse grid collocation for generalized polynomial chaos} \\
  As part of doctorate work, extended RAVEN sampling and reduced-order model methods to include
  sparse grid collocation sampling for multidimensional polynomial surrogate models. Demonstrated
  strengths and weaknesses of algorithm on several analytic as well as real-world problems.
  \item \emph{Developer, RAVEN (github.com/idaholab/raven)} \\
  Trained new users and developers in RAVEN as well as orchestrated signifcant new development and reworks
  of several systems in RAVEN as needs adjusted, managing performance in both memory and speed.
  Responded frequently to user queries, offering guidance or implementing code changes. Reviewed
  proposed code changes for software quality assurance, iterating with developers to improve code
  contributions.
  \item \emph{Python, LaTeX, C++, Conda, Bash}
\end{itemize} \vspace{-6pt}

{\sl Internships} %\\[2pt]
\begin{itemize} \itemsep -2pt
  \item INL: 2012, 2010, MOOSE and MARMOT regression testing
  \item LANL: 2011, Discrete maximum principle for iMC equations
  \item AREVA: 2009, 2008 BLEU effective enrichment research
\end{itemize} \vspace{-6pt}

\vspace{0.2in}
\section{\centerline{ COMPUTING SKILLS }}
\vspace{8pt}
\center{
Extensive use of Python (Conda, Pandas, Xarray, SKLearn, Statsmodels), Git, Bash\\
Experience with C++, MatLab, Visual Basic}

\vspace{0.2in}
\section{\centerline{SAMPLE PUBLICATIONS}}
\vspace{15pt}
\begin{itemize}
  \item H. Wang, R. Ponciroli, A. Alfonsi, P. Talbot, T. Elmer, A. Epiney, R. Vilim,
    ``Feasible Actuator Range Modifier (FARM), a Tool Aiding the Solution of Unit Dispatch Problems for Advanced Energy Systems,''
    Energies 2024; vol 17 no. 12 part F; pp 2945. https://doi.org/10.3390/en17122945
  \item P. Talbot, D. McDowell, B. Rolston, T. Lewis,
    ``Signal Decomposition for Intrusion Detection in Reliability Assessment in Cyber Resilience Summary Report,''
    INL report INL/RPT-23-74252, Idaho National Laboratory, 2023.
  \item M. Basnet, J. Bryan, S. Dana, A. Meek, H. Wang, P. Talbot,
    ``Stochastic Optimization and Uncertainty Quantification of Natrium-Based Nuclear-Renewable Energy Systems for Flexible Power Applications in Deregulated Markets,''
    preprint, available at http://ssrn.com/abstract=4552930.
  \item K. Frick, D. Wendt, P. W. Talbot, et al,
    ``Technoeconomic Assessment of Hydrogen Cogeneration via High Temperature Steam Electrolysis with a Light-Water Reactor,''
    Applied Energy 2022; vol 306 part B, pp. 118044. https://doi.org/10.1016/j.apenergy.2021.118044
  \item Y. Li, A. Sundaram, HS. Abdel-Khalik, P. W. Talbot, ``Real-Time Monitoring for Detection of Adversarial Subtle Process Variations,''
    Nuclear Science and Engineering 2022; pp. 1024.
    \\ https://doi.org/10.1080/00295639.2021.1997041
  \item R. R. Flanagan, P. W. Talbot, et al,
    ``Isolating cloud induced noise to improve generation of synthetic surface solar irradiances,''
    Advances in Applied Energy 2021, vol 3, pp. 100045.
    \\ https://doi.org/10.1016/j.adapen.2021.100045
  \item P. W. Talbot, C. Rabiti, et al, ``Correlated Synthetic Time Series Generation using Fourier and ARMA signal processing,''
    Int. J. Energy Res. 2020; 1-12. https://doi.org/10.1002/er.5115
  \item A. Epiney, C. Rabiti, P. Talbot, et al, "Economic analysis of a nuclear hybrid energy system in a stochastic environment including wind turbines in an electricity grid",
    Applied Energy 2020; 260, 114227
  \item K. Frick, P. Talbot, et al, "Evaluation of Hydrogen Production Feasibility for a Light Water Reactor
	  in the Midwest", INL report INL/EXT-19-55395, 2019
  \item A. Epiney, C. Rabiti, P. Talbot, et al, "Case Study: Nuclear-Renewable-Water Integration in Arizona", INL report INL/EXT-18-51369, 2018
  \item P. W. Talbot, ``Advanced Stochastic Collocation Methods for Polynomial Chaos in RAVEN,'', Ph. D.
    Dissertation, Department of Nuclear Engineering, University of New Mexico, December 2016
  \item P. W. Talbot, C. Wang, et al, ``Multistep Input Reduction for High
    Dimensional Uncertainty Quantification in RAVEN Code,'' ANS PHYSOR 2016
  \item P. W. Talbot, K. Gamble, et al, ``Time-Dependent Sensitivity Analysis of OECD Benchmark using BISON
    and RAVEN,'' 2016 ANS winter conference transactions
  \item P. W. Talbot, A. K. Prinja, C. Rabiti, ``Adaptive Sparse-Grid Stochastic Collocation Uncertainty
    Quantification Convergence for Multigroup Diffusion,'' 2016 ANS annual conference transactions
  \item C. Wang, P. W. Talbot, et al, ``An efficient Sampling-Based Method for Sensitivity and
    Uncertainty Analysis through RAVEN,'' 2016 ANS annual conference transactions
  \item P. W. Talbot, A. K. Prinja, C. Rabiti, ``High Density Model Reduction Uncertainty Quantification
    for Multigroup Diffusion Neutronics,'' 2015 ANS M\&C topical conference transactions
  \item P. W. Talbot, A. K. Prinja, ``Sparse-Grid Stochastic Collocation Uncertainty Quantification Convergence
    for Multigroup Diffusion,'' 2014 ANS winter conference transactions
  \item P. W. Talbot, ``Extending the Discrete Maximum Principle for the IMC equations,'' Oregon State University masters thesis, September 2012
  \item P. W. Talbot, A. B. Wollaber, T. Palmer, ``Implementing a Discrete Maximum Principle for the IMC Equations," 2012 ANS general conference transactions, M \& C division
\end{itemize}
\vspace{10pt}
\begin{itemize}
  \item ORCID: \href{https://orcid.org/0000-0002-9672-9044}{0000-0002-9672-9044}
  \item OSTI: \url{https://www.osti.gov/search/orcid:0000000296729044}
  \item Publons (reviews): \url{https://publons.com/researcher/3839497/paul-talbot/}
\end{itemize}

\vspace{0.2in}
\section{\centerline{MEMBERSHIPS}}
\vspace{-5pt} % reduce space between section title and contents
\begin{itemize}
  \item Reviewer:
  \begin{itemize}
    \item \emph{Applied Energy}
    \item \emph{Energies}
    \item \emph{Mathematics}
    \item \emph{Nuclear Science and Engineering}
    \item \emph{Nuclear Technology}
  \end{itemize}
  \item Conference reviewer: ANS, ANS M\&C\\
  \item Technical Program Committee, ANS M\&C 2019\\
  \item Member, American Nuclear Society
 \end{itemize}

 \begin{center}
	 \emph{References available on request.}
 \end{center}

\end{resume}
\end{document}



%%%%%% EXCESS
\vspace{0.2in}
\section{\centerline{REFERENCES}}
% \vspace{-5pt} % reduce space between section title and contents
\begin{itemize}
  \item Cristian Rabiti, Relationship Manager, Idaho National Laboratory, cristian.rabiti@inl.gov
  \item Andrea Alfonsi, Technical Lead, Idaho National Laboratory, andrea.alfonsi@inl.gov
  \item Anil Prinja, Department Head, University of New Mexico, prinja@unm.edu
 \end{itemize}
 \vspace{0.2in}
%\section{\centerline{INTERESTS}}
%\vspace{-5pt}
%\begin{center}
%scripting and coding, Jazz, family, rock climbing
%\end{center}














